Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/evaluation.tex
upd

@@

The code of ArithOp itself is assumed to operate under a sufficiently
high setting of numeric digits to avoid exponential notation.
\lstinputlisting[language=rexx,label=evaluation\_arithmetic.rexx,caption=evaluation\_arithmetic.rexx]{evaluation\_arithmetic.rexx}

@@

if \#Tracing.\#Level == `I' then call \#Trace
`\textgreater F\textgreater{}' Invocation of a message\_term may result
in a value, in which case: if \#Tracing.\#Level == `I' then call \#Trace
`\textgreater M\textgreater{}'

>>>>

The value of \#Test, in conjunction with the operator in the comparison,
determines the value of the comparison. The value of the comparison is
`1' if - \#Test is `E' and the operator is one of `=``\,``,'==````,
`\textgreater=', \textless='', `\textgreater{}', `\textless{}',
`p\textgreater=', `\textless\textless=', \textgreater\textgreater', or
\textless\textless)

\begin{itemize}
\tightlist
\item
  \#Test is `G' and the operator is one of `\textgreater{}',
  `\textgreater=``, `\textless{}', `=', `\textless\textgreater{}',
  `\textgreater\textless{}', Nes'', `\textgreater\textgreater!
  `p\textgreater{}', or \textless\textless``)
\item
  \#Test is `L' and the operator is one of `\textless{}', \textless=``,
  \textgreater{}`, =', `\textless\textgreater{}',
  `\textgreater\textless{}', ==`,'\textless\textless',
  *\textless\textless=`, or \textgreater\textgreater{}'. In all other
  cases the value of the comparison is `0'.
\end{itemize}

If the comparison is not a concatenation then: if \#Tracing.\#Level ==
`I' then call \#Trace `\textgreater0O\textgreater{}'

@@

The code of ArithOp itself is assumed to operate under a sufficiently
high setting of numeric digits to avoid exponential notation.
\lstinputlisting[language=rexx,label=evaluation-arithmetic.rexx,caption=evaluation-arithmetic.rexx]{evaluation-arithmetic.rexx}

@@

if \#Tracing.\#Level == `I' then call \#Trace
`\textgreater F\textgreater{}'

Invocation of a message\_term may result in a value, in which case:

if \#Tracing.\#Level == `I' then call \#Trace
`\textgreater M\textgreater{}'
